Clean spectral data

### 2020-11-01 R/clean_spectral_data.Rmd
working towards remaking the spectra plot

```{r warning=FALSE, fig.width=12, include=FALSE, eval=FALSE}
# plot spectra to see their starting/ending wavelengths
all_spectra %>% 
  dplyr::filter(spectraID %in% c("NEON.PLA.D07.MLBS.00412_2018", 
                                 "NEON.PLA.D01.HARV.04350_2018",
                                 "NEON.PLA.D08.LENO.08750_2015",
                                 "NEON.PLA.D01.BART.06298_2019")) %>%
  ggplot(aes(x = wavelength_nm, y = reflectance, group = spectraID)) +
  geom_line(aes(color = spectraID), 
            alpha = 0.4) +
  labs(title = "Spectra with different starting wavelengths") + 
  theme_bw()
```

@@

```{r warning=FALSE, fig.width=12}
# plot spectra to see their starting wavelengths
all_spectra %>% 
  dplyr::filter(spectraID %in% c("NEON.PLA.D07.MLBS.00412_2018", 
                                 "NEON.PLA.D01.HARV.04350_2018",
                                 "NEON.PLA.D08.LENO.08750_2015",
                                 "NEON.PLA.D01.BART.06298_2019")) %>%
  ggplot(aes(x = wavelength_nm, y = reflectance, group = spectraID)) +
  geom_line(aes(color = spectraID), 
            alpha = 0.5, size = 1) +
  labs(title = "Spectra with different wavelengths: zoom in on beginning of spectra",
       x = "wavelength [nm]",
       color = "spectrum ID") + 
  # zoom in on beginning of spectra
  lims(x = c(380,400), y = c(0,0.1)) +
  theme_bw()

@@

```{r warning=FALSE, fig.width=12}
# plot spectra to see their ending wavelengths
all_spectra %>% 
  dplyr::filter(spectraID %in% c("NEON.PLA.D07.MLBS.00412_2018", 
                                 "NEON.PLA.D01.HARV.04350_2018",
                                 "NEON.PLA.D08.LENO.08750_2015",
                                 "NEON.PLA.D01.BART.06298_2019")) %>%
  ggplot(aes(x = wavelength_nm, y = reflectance, group = spectraID)) +
  geom_line(aes(color = spectraID), 
            alpha = 0.5, size = 1) +
  labs(title = "Spectra each with different wavelengths: zoom in on end of spectra",
        x = "wavelength [nm]",
       color = "spectrum ID") + 
  # zoom in on end of spectra
  lims(x = c(2455,2515), y = c(0, 0.3)) + 
  theme_bw()

>>>>

```{r warning=FALSE, fig.width=12, include=FALSE, eval=FALSE}
# plot spectra to see their starting/ending wavelengths
all_spectra %>% 
  dplyr::filter(spectraID %in% c("NEON.PLA.D11.CLBJ.00496_2018", 
                                 "NEON.PLA.D01.HARV.09041_2018",
                                 "NEON.PLA.D08.DELA.03903_2017")) %>%
  ggplot(aes(x = wavelength_nm, y = reflectance, group = spectraID)) +
  geom_line(aes(color = spectraID), 
            alpha = 0.4) +
  labs(title = "Spectra with different starting wavelengths") + 
  theme_bw()
```

@@

```{r warning=FALSE, fig.width=12}
# plot spectra to see their starting wavelengths
all_spectra %>% 
  dplyr::filter(spectraID %in% c("NEON.PLA.D11.CLBJ.00496_2018", 
                                 "NEON.PLA.D01.HARV.09041_2018",
                                 "NEON.PLA.D08.DELA.03903_2017")) %>%
  ggplot(aes(x = wavelength_nm, y = reflectance, group = spectraID)) +
  geom_line(aes(color = spectraID), 
            alpha = 0.5, size = 1) +
  labs(title = "Spectra with different wavelengths: zoom in on beginning of spectra",
       x = "wavelength [nm]",
       color = "spectrum ID") + 
  # zoom in on beginning of spectra
  lims(x = c(380,400), y = c(0,0.1)) +
  theme_bw()

@@

```{r warning=FALSE, fig.width=12}
# plot spectra to see their ending wavelengths
all_spectra %>% 
  dplyr::filter(spectraID %in% c("NEON.PLA.D11.CLBJ.00496_2018", 
                                 "NEON.PLA.D01.HARV.09041_2018",
                                 "NEON.PLA.D08.DELA.03903_2017")) %>%
  ggplot(aes(x = wavelength_nm, y = reflectance, group = spectraID)) +
  geom_line(aes(color = spectraID), 
            alpha = 0.5, size = 1) +
  labs(title = "Spectra each with different wavelengths: zoom in on end of spectra",
        x = "wavelength [nm]",
       color = "spectrum ID") + 
  # zoom in on end of spectra
  lims(x = c(2455,2515), y = c(0, 0.3)) + 
  theme_bw()
